Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level. Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm. For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes the boundary cases harder to deal with.

>>>>

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{\}$. Moreover, the worry mentioned above does not get
naturally resolved as in some of these boundary cases, the ratios
between the upper and lower bounds of the gap rise from
$\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such
rise is that, except the first level, we don't have good enough
guarantee of the number of pulls of each arm. For example, in Figure
\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
pulls in the history observed by agents in $G_{l,1,1}$, it could be
that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
the boundary cases harder to deal with.
